Journal and article coverage

### 2025-01-17 analysis/results.Rmd
Fix stat calculation

```{r doi_coverage_check, eval = FALSE}
jn_overlap <- jn_upset |> 
  filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE)

@@

# HOAD
hoad_jn_by_year_ <- active_jns_with_oa |>
  mutate(cr_year = as.numeric(as.character(cr_year))) |>
  distinct(issn_l, cr_year, n_articles = jn_all)
hoad_oa_jn_by_year <- hoaddata::cc_articles |>
  group_by(issn_l, cr_year) |>
  summarise(n_oa_articles = n_distinct(doi))

@@

hoad_ta_df <- hoad_jn_by_year |>
  left_join(hoad_jn_ta_by_year_) |>
  # https://stackoverflow.com/a/73621978
  {\(.) {replace(.,is.na(.),0)}}() |>
  mutate(src = "HOAD") |>
  distinct(issn_l, earliest_year = cr_year, n_oa_articles, n_articles, ta_articles = ta_first_author_articles, ta_first_author_articles, ta_oa_articles = ta_oa_first_author_articles, ta_oa_first_author_articles, src)

@@

```{r plot_uptake, fig.width=8}
# Data prep
uptake_by_year <- uptake_df |>
  mutate(earliest_year = as.character(earliest_year)) |>
  group_by(earliest_year, src) |>
  summarize(
    n_articles = sum(n_articles),
    n_oa_articles = sum(n_oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

@@

```{r}
uptake_jn_five_jns <- uptake_df |>
  filter(earliest_year != "2018") |>
  group_by(issn_l, src) |>
  summarize(
    n_articles = sum(n_articles),
    n_oa_articles = sum(n_oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

@@

uptake_publisher_by_year <- uptake_publisher |>
  mutate(earliest_year = as.character(earliest_year)) |>
  group_by(earliest_year, src, publisher) |>
  summarize(
    n_articles = sum(n_articles),
    n_oa_articles = sum(n_oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

>>>>

```{r doi_coverage_check, eval = FALSE}
jn_overlap <- jn_upset_articles |> 
  filter(Crossref == TRUE, WoS == TRUE, Scopus == TRUE)

@@

# HOAD
hoad_jn_by_year_ <- active_jns_with_oa |>
  mutate(cr_year = as.numeric(as.character(cr_year))) |>
  distinct(issn_l, cr_year, n = jn_all)
hoad_oa_jn_by_year <- hoaddata::cc_articles |>
  group_by(issn_l, cr_year) |>
  summarise(oa_articles = n_distinct(doi))

@@

hoad_ta_df <- hoad_jn_by_year |>
  left_join(hoad_jn_ta_by_year_) |>
  # https://stackoverflow.com/a/73621978
  {\(.) {replace(.,is.na(.),0)}}() |>
  mutate(src = "HOAD") |>
  distinct(issn_l, earliest_year = cr_year, n, oa_articles, ta_articles = ta_first_author_articles, ta_first_author_articles, ta_oa_articles = ta_oa_first_author_articles, ta_oa_first_author_articles, src)

@@

```{r plot_uptake, fig.width=8}
# Data prep
uptake_by_year <- uptake_df |>
  mutate(earliest_year = as.character(earliest_year)) |>
  group_by(earliest_year, src) |>
  summarize(
    n_articles = sum(n),
    n_oa_articles = sum(oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

@@

```{r}
uptake_jn_five_jns <- uptake_df |>
  filter(earliest_year != "2018") |>
  group_by(issn_l, src) |>
  summarize(
    n_articles = sum(n),
    n_oa_articles = sum(oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

@@

uptake_publisher_by_year <- uptake_publisher |>
  mutate(earliest_year = as.character(earliest_year)) |>
  group_by(earliest_year, src, publisher) |>
  summarize(
    n_articles = sum(n),
    n_oa_articles = sum(oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )
